Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2017-03-10 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
ch 8
?

Mc caffery plume

@@

@@

>>>>

%Mc caffery plume    
%continuous flame region 
%intermittant flame region
%plume region

@@

\subsubsection{Radiative Fraction}

From Chapter 2 the

@@

The next comparsions will be made with the natural gas source fire at 4 different distance from an gypsum board wall.  Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).  The simulations will replicate the same distances.  The simulation includes a vertical gypsum board wall, 1.2~m wide, that extends from the floor of the model up to the top of the domain.  The material properties of the wall are based solely on the properties of gypsum that were cited in Chapter

\subsubsection{Input Data Natural Gas Instrumented Wall Fires}

The computational domain of the model was the same as the volume considered for the source fire simulations, a cube with 2.4~m on a side.
